%The abstract must contain 3 main logic blocks which will be discussed in the introduction.

%Field of work
%The first block must contain a sentence which describes the field of work, and eventually another sentence which focuses the specific objective of the work in details.

%Purpose of the thesis
%The second block must start with the words «The purpose of the thesis is …».

%Short recap
%The last block must summarize the conducted activities and the obtained results (evaluating them eventually).

This thesis is about the synchronized flight of a formation of multirotors which executes a mission.
The mission is characterized by a trajectory for every drone which composes the formation.
The formation must be able to deal with unforeseen events, which can compromise
the outcome of the mission. In order to do that, the drones must exchange information
between each others, therefore a support network is needed.

The purpose of this thesis is to present the algorithm for synchronized formation flight
called “Consensus algorithm” and implement it in a simulated environment
and in a real system with heterogeneous drones. We want to verify that the theoretical
results can be applied in a real distributed system, with not ideal network performances.

In the first part, we explain the algorithm used during the experimental work,
while in the following chapter the software and hardware used are presented.
In the last chapters we show in detail the structure of the software and the experiment conducted.
In particular, many simulations will be presented to confirm the quality of the
“Consensus algorithm”. Finally, a comparison between the simulated results and the ones
obtained in the real environment is proposed.
