%%Introduction of the chapter
The literature about the "Consensus" has grown significantly in the latest years
because of the increasing presence of autonomous vehicles. This, in accordance with
the new improvements in robotics, has brought to growing interest in consensus
between multiple agents which have to accomplish a mission in cooperative or adversarial
scenarios.

The "Consensus" theory has its roots in Graph Theory and Automatics and it can
be used to coordinate a mission in order to achieve the synchronization between
the vehicles even during unforeseen events which force one or more
components of the mission to change the planned trajectory or task. In this case,
the other components identify this variation and they act to preserve the
synchronization.

The "Consensus" algorithm is a distributed algorithm which can sometimes be simulated
in a centralized fashion because of the reduced computational power of the machines
involved in the mission, which are equipped with low power hardware to account for
the crucial issue of power consumption.
In this scenario, a centralized server simulates the algorithm and communicates with
all the machines.

The most common "Consensus" application is a spatial and timing consensus: in this
implementation, each vehicle of the formation has to travel along a specified trajectory and the
completion of the mission occurs when all the agents reach the final positions of their
spatial paths. The algorithm has to guarantee that the difference between
the ending time at which all the vehicles finish their tasks is minimized and
asymptotically goes to zero, when the execution time goes to infinity and no other
unforeseen events happens.
We also consider formations of Unmanned Aerial Vehicles, but the key concepts can
be freely applied to other categories of robots when they are able to follow a trajectory.
This study is focused on this kind of application, and further
simulation results and experimental achievements are presented in chapters
\ref{chap:simulation_results} and \ref{chap:experimental_results}.

In the next sections we refer to the main work of Venanzio Cichella \cite{cichellaMain}
in the field of UAV consensus, in order to provide an homogeneous state of the art
about the "Consensus".
The paper considers all the details needed to build a "Consensus" system.
The main components of this kind of system are listed and explained below:
\begin{itemize}
  \item Parametrized trajectory
  \item Virtual time
  \item Consensus law
  \item Network topology
\end{itemize}



%% Sections of the chapter
\input{chapters/chapter-01/parametrized_trajectory.tex}

\input{chapters/chapter-01/virtual_time.tex}

\input{chapters/chapter-01/consensus_law.tex}

\input{chapters/chapter-01/network_topology.tex}

\input{chapters/chapter-01/convergence_property.tex}
