\section{Virtual time\label{sec:virtual_time}}

Given $ N $ collision free trajectories, we want each vehicle to follow a \textit{virtual target},
moving along the path computed offline by the trajectory generation algorithm.
The objective can be achieved introducing a \textit{virtual time}, $ \gamma_i $,
which is used to evaluate the trajectory and can be adjusted online to reach
the synchronization even when external disturbances occur.
Thus, the position of the $ i^{th} $ virtual target is denoted by $ p_{d,i} ( \gamma_i (t))$
and the $ i^{th} $ vehicle tries to follow it, by reducing to zero a suitably defined
error vector using control inputs.

Considering the trajectory $ p_{d,i} (t_d) $ produced by the trajectory generation
algorithm, we consider the virtual time $ \gamma_i $ as a function of time $ t $,
which relates the actual time $t$ to mission planning time $t_d$.

\begin{equation}  \label{eq:virt_time_func}
  \gamma_i : \mathbb{R}^+ \rightarrow [0, T_d], \qquad for \; all \quad i = 1,2,\dots,N
\end{equation}

We can now define the virtual target's position, velocity and acceleration, which
have to be followed by the $ i^{th}$ vehicle at time $t$

\begin{equation}  \label{eq:pos_vel_acc_def}
  \begin{aligned}
  p_{c,i}(t) = \ & p_{d,i}(\gamma_i(t)) \\
  v_{c,i}(t) = \ & \dot{p}_{d,i} (\gamma_i(t), \dot{\gamma}_i (t)) \\
  a_{c,i}(t) = \ & \ddot{p}_{d,i} (\gamma_i(t), \dot{\gamma}_i(t), \ddot{\gamma}_i(t))
  \end{aligned}
\end{equation}

With the above formulation, if $ \dot{\gamma} = 1$, then the speed profile of
the virtual target is equal to the desired speed profile computed at trajectory
generation level.
Indeed, if $ \dot{\gamma} = 1$, for all $t \in [0, T_d]$, with $\gamma_i(0) = 0$,
it implies that $\gamma_i(t) = t_d$ for all $t$ and thus:

\begin{equation*}
  p_{c,i}(t) = p_{d,i}(\gamma_i(t)) = p_{d,i}(t) = p_{d,i} (t_d)
\end{equation*}

In this particular case, the desired and commanded trajectories coincide
in every time instant and also the velocity profiles coincide with the ones
chosen at the trajectory generation time.
If instead $\dot{\gamma_i} > 1$, it implies a faster execution of the mission;
on the other hand, $\dot{\gamma_i} < 1$ implies a slower one.

We can now normalize $\gamma_i$ in order to have a range which is $[0,1]$. We simply
need to divide all by $T_d$. In this way, we could use Bezier curves in order to
represent the spatial path. This kind of curves offer interesting properties for
computing minimum distances between two of them and allow the computation of
smooth trajectories. In any case, it is not mandatory to use them and a general
function could be used instead.

The second order derivative of $\gamma_i$, $\ddot{\gamma}_i$, is a free parameter
used to achieve the consensus. In the next section we will introduce the control law
which commands its evolution during time and we will explain how it is possible to
implement a distributed algorithm.
